Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
draft: on metrics

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}

@@

\subsection{Metrics}

>>>>

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{bbm}
\usepackage[ruled]{algorithm2e}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}

@@

\subsection{Metrics}
We evaluate the performance of the different approaches by measuring the coverage of the phenomenon over time.
%
The coverage is defined as the percentage of the phenomenon covered by the agents.
%
Specifically, we can measure the coverage as the intersection over the union of the phenomenon and the agents' view range.
%
Formally, first, we define the overall area covered by the agents as:
\begin{equation*}
\Omega = \bigcup_{v \in V} \omega_v
\end{equation*}

Finally, we define the coverage as:
\begin{equation*}
C = \frac{|\Omega \cap \mathcal{P}|}{|\mathcal{P}|}
\end{equation*}
where $\omega$ is the viewing range of the agents and $\mathcal{P}$ is the phenomenon.
This is computed for each step of the simulation.

We also measure the number of agents that are within the phenomenon at each step of the simulation.
This will be a measure of how well the agents are tracking the phenomenon.
\ga{todo improve the description of the coverage}
